Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens

### 2014-01-26 limits/ms.tex
Improved font in some plots. Updated captions.

\def\newblock{\hskip .11em plus .33em minus .07em}

@@

\title[Lens Recovery with \Glass]{Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens}
\author[J.~P.~Coles~et~al.]{%
Jonathan P.~Coles,$^{1,3}$\thanks{jonathan@exascale-computing.eu}%
\newauthor%
Justin I.~Read$^2$,%
\newauthor%
and Prasenjit Saha$^3$%
%
\\
$^1$Exascale Research Computing Lab, Versailles Saint-Quentin-en-Yvelines University,\\$\quad$55 Avenue des Etats Unis, 78000, Versailles, France\\
$^2$Department of Physics, University of Surrey, Guildford, Surrey, GU2 7XH, United Kingdom \\
$^3$Institute of Physics, University of Zurich, 190 Winterthurerstrasse, 8057, Zurich, Switzerland
}

@@

%(Linear constraints are applied simultaneously with the lens constraints; non-linear constraints are applied in post-processing, with models accepted or rejected based on their likelihood.) 
%These are quantities of key interest for probing the dark matter distribution in galaxies and galaxy clusters to test galaxy formation models and cosmology.

\section{Introduction}\label{sec:intro} %-----------------------------------------------------

@@

% since distant light source in the universe rarely goes through a region such that the projected density in its sky neighbourhood exceeds the critical density to produce multiple images.

@@

GOT TO HERE.

@@

% Simple parametric models are usually robust on qualitative features,
% but other aspects can be very model-dependent
% \citep[cf.~][]{2003AJ....125.2769S}.  For example, for lensed
% quasars, there may be several models all providing excellent fits to
% the image data but disagreeing on the expected time delays, but they
% almost always agree about the {\em order\/} of time delays. Thus, a
% simple model provides valuable physical insight, but as data quality
% improves and the questions we ask of these data become more refined,
% it is important to re-assess the impact of our model assumptions.
% The key advantages of non-parametric modelling are that we can: (i)
% explore model degeneracies and marginalise over them; and (ii) we
% can determine what type and quality of data are required to measure
% parameters of interest.

@@

@@

% The only lensing observables from \eqnref{arrival time} are the
% image positions. However, if the source object is variable then the
% observed light curves of each image will be identical but shifted in
% time due to the different photon path lengths.  The time difference
% between identical portions of the light curves is called the time
% delay $\Delta t$ between images.  Using \eqnref{tau} the time delay
% $\Delta t_{21}$ between two images $\vec\theta_1$ and
% $\vec\theta_2$, where $\vec\theta_2$ arrives after $\vec\theta_1$,
% is $\Delta t_{21} = \Delta \tau_{21}(1+z_L)d_L / \zeta$. If $\beta$
% and $\kappa_\infty$ could be known exactly this would allow one to
% precisely infer the angular diameter distance to the lens and thus
% -- via a cosmological model -- the Hubble constant. However, the
% source position is not observable and the density distribution is
% highly degenerate.

% \subsection{Degeneracies}\label{sec:degen}
%
% The trouble with solving the lens equation for the mass distribution is that the solutions are not unique. To see why, it is instructive to simplify \eqnref{eqn:lens_equation} for a circularly symmetric lens: 
%
% \begin{equation}
% \vec\beta = \vec\theta - \frac{\theta_E^2}{\theta^2}\vec\theta
% \label{eqn:lens_equation_circ}
% \end{equation}
%
% where $\theta = |\vec\theta|$, $\theta_E^2 = \frac{D_{LS}}{D_S D_L} \frac{4 GM(<\theta)}{c^2}$ is the Einstein radius, and $M(<\theta)$ is the mass enclosed within the images.

% For on-axis sources (\vec\beta\ = \vec0), the images split into a degenerate Einstein ring with $\theta = \theta_E$. Even in this situation of maximal information (since the source position $\vec\beta$ cannot typically be known), there is a trivial degeneracy between $M(<\theta_E)$ and the angular diameter distance. For fixed cosmology and in the most ideal situation, a single source splitting into images gives us only an enclosed mass. This `steepness' degeneracy (also known as the mass-sheet degeneracy) generalises to the non-circularly symmetric case \citep{1985ApJ...289L...1F,2000AJ....120.1654S}. Thus, to measure the mass profile of a lens, we require more information. This can come in the form of sources at different redshifts -- since each has its own Einstein radius, each constrains a different enclosed mass $M(<\theta_E')$. Or it can come in the form of additional constraints like time delay data between the images, stellar mass estimates from stellar populations synthesis modelling \citep{2008MNRAS.383..857F}, stellar kinematics \citep{2002MNRAS.337L...6T}, or similar. However, even with further information, higher order degeneracies remain. \citet{2008MNRAS.386..307L} showed that there is a monopole degeneracy that allows additional mass to be deposited in-between images without any optical effect, while \citep{2006ApJ...653..936S} find twisting/shape degeneracies that are sensitive to the time delays. Further degeneracies enter also if there is a strong {\it external} field acting on the lens -- for example from a larger group or cluster environment within which the lens sits \citep[e.g.][]{1996ApJ...468...17B}. However, this {\it shear term} can be constrained by data \citep[e.g.][]{2002ApJ...578...25K}. In \secref{sec:results}, we will use \Glass\ to determine how well such degeneracies can be broken by data of ever-increasing quality to measure the mass profile and shape of a lens. We assume throughout that the shear is negligible.

% {\bf Is ``Schneider's degeneracy" something new? Should we cite it here? -- {\tt http://adsabs.harvard.edu/abs/2013arXiv1306.4675S}}

@@

\Glass is the Gravitational Lensing AnalysiS Software. It is an evolution of the concepts employed by the free form modelling tool
\PixeLens\ but completely rewritten in Python and C. 
The most compute intensive
portion was written in C but Python was chosen because of its flexibility as a 
language and for its large scientific library support. The flexibility allows 
\Glass\ to have quite sophisticated behavior while at the same time simplifying the 
user experience and reducing the overall development time. One of the striking
features is that the input file to \Glass\ is itself a Python program.
Understanding Python is not necessary for the most basic use, but this allows
a user to build complex analysis of a model directly into the input file. \Glass\
may also be used as an external library to other Python programs.  The software
is freely available for download or from the author%
%
\footnote{Currently hosted on GitHub: www.github.com/jpcoles/glass or through
www.jpcoles.com/glass.}.

@@

%\Glass\ uses an adaptive grid of mass pixels
%to model the lens, generating thousands of models to marginalise over
%uncertainties. It shares some heritage with an earlier code, \PixeLens\
%\citep{1997MNRAS.292..148S,2008ApJ...679...17C}, but differs in several
%important respects: 
%\begin{enumerate} 
%\item it uses a significantly improved sampling strategy that is both faster and results in significantly smaller errors \citep{2012MNRAS.425.3077L};
%\item it is built on a fully modular framework that can support different basis functions;
%\item non-linear constraints can be applied in post-processing (for example, filters to remove models with spurious additional images or models inconsistent with stellar dynamics data are already implemented);
%\item the stellar mass (if known) can be applied as a prior; and
%\item adaptive resolution can be used in regions of interest. 
%\end{enumerate}
%This new functionality allows us to include non-lensing data constraints. Linear constraints -- like the stellar
%mass -- are applied simultaneously with the strong lensing constraints;
%non-linear constraints are applied in a post-processing step, where models are
%rejected using a likelihood analysis. This latter was prohibitively expensive
%with \PixeLens\ as only up to $\sim$1000 models could be generated in a
%reasonable time. With \Glass, we can routinely generate hundreds of thousands
%of models such that we can afford to discard some if they are inconsistent with
%independent data.

@@

%
%\begin{equation}
  %\psi^*(\vec\theta) = \sum_n \kappa^*_n Q_n(\vec\theta)\quad.
%\end{equation}
%

@@

\subsection{Lens configurations}\label{sec:lensconfig} %--------------------------------------------------------------

@@

\begin{figure*}
  \plotthree{BCExtendedDoubleR1_tms-a.pdf} {BCExtendedDoubleR1_tms-b.pdf} {BCExtendedDoubleR1_tms-c.pdf}
  \plotthree{BCExtendedDoubleR1_tmS-a-1.pdf} {BCExtendedDoubleR1_tmS-b-1.pdf} {BCExtendedDoubleR1_tmS-c-1.pdf}
  \plotthree{BCQuadR1a_Tms-a.pdf} {BCQuadR1a_Tms-b.pdf} {BCQuadR1a_Tms-c.pdf}
  \plotthree{AAQuadR1a_Tms-a.pdf} {AAQuadR1a_Tms-b.pdf} {AAQuadR1a_Tms-c.pdf}
\caption{
  \hilight{Larger fonts. Do we need both examples?}
Two typical reconstructed lens. Here we present results for a single quad image lensed by the \mockBC{} (upper) and \mockAC{} (lower) mock galaxies.
\textbf{Left:}
The ensemble average arrival time surface, with just the isocontours for the
saddle points drawn. The central diamonds show the reconstructed source
position across the entire ensemble.
\textbf{Middle:}
The surface density. The magenta curve represents the dark matter component,
the yellow curve the stellar component, and the blue curve is the sum of the two.
The black curve comes from the original mass model used to create the lens.
The vertical lines mark the radial positions of the images. The higher
resolution feature of \Glass\ has been used on the central pixel allowing the
steep profile to be captured.
\textbf{Right:}
The cumulative mass. The error bars on all plots are $1\sigma$, but the grey area shows the full range for DM+Stars (blue).}
\label{reconstruction}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-a.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
\caption{ \textbf{Left:} The mock data distribution for \mockBC{} projected onto a coarse grid.
  \textbf{Right:} The recovered ensemble average $\kappa$ distribution for the single quad. The contours are
  logarithmic values, where level 0 corresponds to the critical density. Contours below the critical density
  are drawn with dashed lines.}
\label{2d mass reconstruction}
\end{figure*}

The main results from modeling these different configurations are shown in
\figref{main results} and \figref{main results pixel-wise}. Each
subplot corresponds to a different mock galaxy. We show the fractional error of the mass
distribution for each of the test configurations with (red) and without stellar mass (black)
In \figref{main results}, the error is defined over radial bins of mass as
%
\begin{equation} \label{ferror R}
  f_R = \frac {\sum_i \left|M(i) - \tilde M(i)\right| } {\sum \tilde M(i)}
\end{equation}
%
where $M$ is the mass in bin $i$ and $\tilde M$ is the mass from the mock galaxy.
In \figref{main results pixel-wise} the error is defined over all the pixels $\vec\theta$
%
\begin{equation} \label{ferror theta}
f_\theta = \frac {\sum_{\vec\theta} \left|M(\vec\theta) - \tilde M(\vec\theta)\right| } {\sum_{\vec\theta} \tilde M(\vec\theta)}
\end{equation}
%
%\begin{equation}
%  \chi_i \equiv 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
%\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
%\end{equation}
%where $\rho_{\M_i}(r)$ is the recovered density profile for a mock model $\M_i$; and $\rho_G(r)$ is the true density profile.

@@

\begin{figure}
\plottwo{AAExtendedDoubleR1_TmS-shape-hist.pdf}{BCZContrastR1R3_TmS-shape-hist.pdf}
\caption{ \hilight{Larger labels.} The two plots in the left most column show sample distributions of
  $s=\lambda_1/\lambda_2$, the ratio of the largest to smallest principal axes.
  The upper (poor) plot is from the \mockAA{} galaxy, while the lower (good) plot is
  from the \mockBC{} galaxy. The black vertical lines mark the $2\sigma$
  region and the vertical blue line is the value of $s$ for the corresponding
mock galaxy. }

@@

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_Tms_sigp-1.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS_sigp-2.pdf}
\includegraphics[width=0.33\textwidth]{BC_beta.pdf}
\caption{ \hilight{Larger fonts.} Estimated projected radially averaged velocity dispersion $\sigma_p$
\eqnrefp{eqn:sphericaljeans} for a single quad from the \mockBC{} mock galaxy without stellar mass
(\textbf{left}) and with stellar mass (\textbf{middle}) assuming an anisotropy $\beta=0$
(blue, solid) and $\beta=1$ (blue, dashed).  The equivalent
curves are also shown for the projected mock data after using the same analysis routines
(purple). The solid black line is the actual cylindrically averaged velocity
dispersion of the original mock particle data.  The stellar half mass radius
(yellow) Einstein radius (black) are marked by vertical lines. For this
configuration, these two radii are well-separated. The actual variation in $\beta(r)$ is show also shown (\textbf{right}).}

@@

\hilight{This is a bit overstated.}
With the stellar mass lower bound, the improvement of the reconstruction
quality shown in \figref{main results} is quite dramatic for the doubles in the 
steepest mock galaxies (\mockAC{} and \mockBC). This is because these models are dominated
by stars in the inner region. By contrast, the other two galaxies -- where the stars contribute negligibly to the potential -- are unaffected.

@@

%\begin{figure*}
%\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
%\includegraphics[width=0.49\textwidth]{BCQuadR1a_TmS_sigpbar.pdf}
%\caption{{\bf Left:} 
%The mean projected velocity dispersion (\eqnref{eqn:virialaverage}) as a function of the upper
%limit of the averaging integral (the aperture size), $a_p$
%  for two Sdom/DMcuspy models ZContrastR1R3
%  (left) and QuadR1a (right) assuming two extrema velocity anisotropies $\beta=0$ (blue, solid) and $\beta=1$
%  (blue, dashed).  Also shown are the equivalent curves for the mock data after
%  running it through the deprojection routines (grey). 
%\sout{Over-plotted is the correct answer for the BC model (black)
%  {\bf JR. Jonathan to add}.} 
%  The stellar half mass radius (yellow) Einstein
%radius (black) are marked by vertical lines. For this configuration, these two
%radii are well-separated.}
%\label{sigma-beta}
%\end{figure*}

%\subsection{Velocity dispersions}
%
%\begin{itemize}
%\item Can they predict radial profiles?
%\item Can we constrain lensing models from predicted velocity dispersions?
%\item Use a constructed spherical halo G2 following a $\rho \propto r^{-\gamma}$ profile with stellar halo same as G1.
%\item Vary $z$ of the halo, possibly orientation.
%\item Should be able to recover $\gamma$ very well.
%\item Use G1. Show problems with recovering $\gamma$.
%\end{itemize}

%\subsection{With/without time delays and central image} %--------------------------------------------------------------

%We also considered the effect of having time delays or a central image. The
%central image is usually highly demagnified and obscured by the lensing galaxy,
%but in clusters the central image is observable. In this case we can imagine
%the galaxies to be clusters since the problem is scale-free. A recontruction of
%AASingleQuadR1a\_Tm is shown in \figref{AASingleQuadR1a_Tm}. The suffix denotes
%which combination of time delays (T) and central image (M) was used. An
%uppercase letter indicates the feature is turned on, and a lowercase letter
%that it is turned off.

@@

\section{Raytracing convergence test}
Raytracing is sensitive to the map area and resolution set by $\Rmap$ and
$\Rpix$.  In the left panel of \figref{raytracing convergence tests} we compare
the change in time delays as we increase $\Rmap$.  The image system is a quad
with the central maximum image. When the projected mass begins to fall off the
time delays stabilize. In the right panel we see the effect of changing the
resolution of the map.  Increasing the resolution allows for more accurate
placement of the images and after about $\Rpix=40$ the image positions change
by less than 0.04 arcsec. The one image that continues to change is near to a
caustic.

\begin{figure}
\plottwo{tdconv_pr45.pdf}{imgpos_conv_mr20.pdf}
\caption{\textbf{Left:} Test for convergence of the predicted time delay as $\Rmap$ is increased and
$\Rpix=45$ is held constant. After about $\Rmap=20$ most of the asymmetric mass is in the map.
\textbf{Right:} Test for convergence of the predicted image positions $\theta$ as $\Rpix$
changes and $\Rmap=20$ arcsec is held constant.}
\label{raytracing convergence tests}
\end{figure}

>>>>

@@

\title[Lens Recovery with \Glass]{Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens}
\author[J.~P.~Coles~et~al.]{%
Jonathan P.~Coles,$^{1,3}$\thanks{jonathan@exascale-computing.eu}%
\newauthor%
Justin I.~Read$^2$,%
\newauthor%
and Prasenjit Saha$^3$%
%
\\
$^1$Exascale Research Computing Lab, Universit\'e de Versailles Saint-Quentin-en-Yvelines,\\$\quad$55 Avenue des Etats Unis, 78000, Versailles, France\\
$^2$\hilight{Department of Physics, University of Surrey, Guildford, Surrey, GU2 7XH, United Kingdom} \\
$^3$\hilight{Institute of Physics, University of Zurich, 190 Winterthurerstrasse, 8057, Zurich, Switzerland}
}

@@

\section{Introduction}\label{sec:intro}

@@

@@

\hilight{GOT TO HERE. }

@@

@@

%

@@

@@

\Glass is the Gravitational Lensing AnalysiS Software. It is an evolution of the concepts employed by the free form modelling tool
\PixeLens\ but completely rewritten in Python and C. 
The most compute intensive
portion was written in C but Python was chosen because of its flexibility as a 
language and for its large scientific library support. The flexibility allows 
\Glass\ to have quite sophisticated behavior while at the same time simplifying the 
user experience and reducing the overall development time. One of the striking
features is that the input file to \Glass\ is itself a Python program.
Understanding Python is not necessary for the most basic use, but this allows
a user to build complex analysis of a model directly into the input file. \Glass\
may also be used as an external library to other Python programs.  The software
is freely available for download or from the author%
%
\footnote{http://www.jpcoles.com.}.

@@

@@

@@

\subsection{Lens configurations}\label{sec:lensconfig}

@@

\begin{figure*}
  \plotthree{BCExtendedDoubleR1_tms-a.pdf} {BCExtendedDoubleR1_tms-b.pdf} {BCExtendedDoubleR1_tms-c.pdf}
  \plotthree{BCExtendedDoubleR1_tmS-a-1.pdf} {BCExtendedDoubleR1_tmS-b-1.pdf} {BCExtendedDoubleR1_tmS-c-1.pdf}
  \plotthree{BCQuadR1a_Tms-a.pdf} {BCQuadR1a_Tms-b.pdf} {BCQuadR1a_Tms-c.pdf}
  \plotthree{AAQuadR1a_Tms-a.pdf} {AAQuadR1a_Tms-b.pdf} {AAQuadR1a_Tms-c.pdf}
\caption{
    Four reconstructed lenses. The first two rows consider the same mock
    galaxy, \mockBC, for an extended double, and highlight the improved
    constraints on the mass distribution when a lower bound is given by the
    stellar mass. For the reconstruction, no time delays were assumed.  The
    third row uses again the the \mockBC{} mock galaxy, but with time delays
    for a single quad and no stellar mass. With the added information from the
    quad, the outer regions of the lens are the image radii are better
    constrained. Finally, the fourth row shows another case of a quad with time
    delays, but using the \mockAA{} mock galaxy. This galaxy has a shallower
    stellar density index, and a core in the dark matter. Due to the priors
    used in \Glass, the modelling favors steep solutions without additional
    information.
\textbf{Left:}
The ensemble average arrival time surface with just the isocontours for the
saddle points drawn. The central diamonds show the reconstructed source
position.
\textbf{Middle:}
The surface density of the dark matter (magenta), the stars (yellow), and the total (blue).
The original mass model used to create the lens is shown in black.
The vertical lines mark the radial positions of the images. The higher
resolution feature of \Glass\ has been used on the central pixel allowing the
steep profile to be captured.
\textbf{Right:}
The cumulative mass. The error bars on all plots are $1\sigma$, but the grey area shows the full range of models for DM+Stars (blue).}
\label{reconstruction}
\end{figure*}

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-a.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS-kappa-b.pdf}
\caption{ \textbf{Left:} The mock data distribution for \mockBC{} projected onto a coarse grid.
  \textbf{Right:} The recovered ensemble average $\kappa$ distribution for the single quad. The contours are
  logarithmic base 10 values, where level 0 corresponds to the critical density. Contours below the critical density
  are drawn with dashed lines.}
\label{2d mass reconstruction}
\end{figure*}

The main results from modeling these different configurations are shown in
\figref{main results} and \figref{main results pixel-wise}. Each
subplot corresponds to a different mock galaxy. We show the fractional error of the mass
distribution for each of the test configurations with (red) and without stellar mass (black)
In \figref{main results}, the error is defined over radial bins of mass as
%
\begin{equation} \label{ferror R}
  f_R = \frac {\sum_i \left|M(i) - \tilde M(i)\right| } {\sum \tilde M(i)}
\end{equation}
%
where $M$ is the mass in bin $i$ and $\tilde M$ is the mass from the mock galaxy.
In \figref{main results pixel-wise} the error is defined over all the pixels $\vec\theta$
%
\begin{equation} \label{ferror theta}
f_\theta = \frac {\sum_{\vec\theta} \left|M(\vec\theta) - \tilde M(\vec\theta)\right| } {\sum_{\vec\theta} \tilde M(\vec\theta)}
\end{equation}

@@

\begin{figure}
\plottwo{AAExtendedDoubleR1_TmS-shape-hist.pdf}{BCZContrastR1R3_TmS-shape-hist.pdf}
\caption{The two plots in the left most column show sample distributions of
  $s=\lambda_1/\lambda_2$, the ratio of the largest to smallest principal axes.
  The upper (poor) plot is from the \mockAA{} galaxy, while the lower (good) plot is
  from the \mockBC{} galaxy. The black vertical lines mark the $2\sigma$
  region and the vertical blue line is the value of $s$ for the corresponding
mock galaxy. }

@@

\begin{figure*}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_Tms_sigp-1.pdf}
\includegraphics[width=0.33\textwidth]{BCQuadR1a_TmS_sigp-2.pdf}
\includegraphics[width=0.33\textwidth]{BC_beta.pdf}
\caption{ Estimated projected radially averaged velocity dispersion $\sigma_p$
\eqnrefp{eqn:sphericaljeans} for a single quad from the \mockBC{} mock galaxy without stellar mass
(\textbf{left}) and with stellar mass (\textbf{middle}) assuming an anisotropy $\beta=0$
(blue, solid) and $\beta=1$ (blue, dashed).  The equivalent
curves are also shown for the projected mock data after using the same analysis routines
(purple). The solid black line is the actual cylindrically averaged velocity
dispersion of the original mock particle data.  The stellar half mass radius
(yellow) Einstein radius (black) are marked by vertical lines. For this
configuration, these two radii are well-separated. The actual variation in $\beta(r)$ is show also shown (\textbf{right}).}

@@

\hilight{This is a bit overstated.}
With the stellar mass lower bound, the improvement of the reconstruction
quality shown in \figref{main results} is quite dramatic for the doubles in the
steepest mock galaxies (\mockAC{} and \mockBC). This is because these models
are dominated by stars in the inner region. By contrast, the other two galaxies
---where the stars contribute negligibly to the potential---are unaffected.

@@

@@

%\section{Raytracing convergence test}
%Raytracing is sensitive to the map area and resolution set by $\Rmap$ and
%$\Rpix$.  In the left panel of \figref{raytracing convergence tests} we compare
%the change in time delays as we increase $\Rmap$.  The image system is a quad
%with the central maximum image. When the projected mass begins to fall off the
%time delays stabilize. In the right panel we see the effect of changing the
%resolution of the map.  Increasing the resolution allows for more accurate
%placement of the images and after about $\Rpix=40$ the image positions change
%by less than 0.04 arcsec. The one image that continues to change is near to a
%caustic.  
%
%\begin{figure}
%\plottwo{tdconv_pr45.pdf}{imgpos_conv_mr20.pdf}
%\caption{\textbf{Left:} Test for convergence of the predicted time delay as $\Rmap$ is increased and
%$\Rpix=45$ is held constant. After about $\Rmap=20$ most of the asymmetric mass is in the map.
%\textbf{Right:} Test for convergence of the predicted image positions $\theta$ as $\Rpix$
%changes and $\Rmap=20$ arcsec is held constant.}
%\label{raytracing convergence tests}
%\end{figure}
